Attribute fusion in a latent process model for time series of graphs

### 2011-05-13 ssp2011.tex
Add some mention of Rukhin&Priebe work for scan

    a_n &= N_{0} \frac{\langle \lambda, \pi_{00} \rangle}{\langle
      1, \pi_{00} \rangle} + C_{00}p_{00}\tbinom{N_{0}}{2} \\ 
   b_n &= (1 - \tfrac{C_{00}p_{00}}{2} + C_{00}p_{00} N_{0}) \frac{\sigma_0}{\sqrt{2 \log

@@

@@

    a_{n,m} &=%  N_{\kappa} \frac{\langle x, \pi_{01} \rangle}{\langle

@@

    C_{00} p_{00} \Bigl(\tbinom{N_\kappa}{2} - \tbinom{\mu_E}{2} - \mu_E
    \mu_F\Bigr) \\ 
     & + C_{11} p_{11} \tbinom{\mu_E}{2} + C_{01} p_{01} \mu_E \mu_F 

@@

    b_{n,m} = (1 - \tfrac{C_{00} p_{00}}{2} + C_{00} p_{00}
    N_\kappa)\frac{\sigma_{E + F}}{\sqrt{2 \log{n_1}}}

@@

    \mathbb{P}[ \frac{X - \mu}{\sigma} \leq z]  &= \mathbb{P}[X \leq z

@@

  mean and the sample variance are consistent estimators, the claims
  follow after an application of Slutsky's theorem.

@@

$\phi_\lambda(v)$ for our
attributed random graphs model at time $t = t^{*}$ can be approximated by
the locality statistics $Y(v)$ for an unattributed kidney and egg
model. Let $G$ be an instance of $\kappa(n,m,p_{11},
p_{10}, p_{00})$, an unattributed kidney-egg graph with the
probability of egg-egg, egg-kidney, and kidney-kidney connections
being $p_{11}$, $p_{10}$, and $p_{00}$, respectively. $D(v) = M(v) + W(v)$ is then the degree
of $v$ in $G$. We now show two
inequalities relating the tail distribution of 

@@

We first consider the term $a_{n,m} - g(v)$. We have

@@

for some $a > 0$. The set $\{v \in [m]\}$ can now be partitition into

@@

o(n^{-1})$ by using a concentration inequality, e.g., Hoeffding's

@@

    p_{S_3} \leq \sum_{\{e,f\} \in S_3} \mathbb{P} \Bigl[Z \leq

>>>>

  %  a_n &= N_{0} \frac{\langle \lambda, \pi_{00} \rangle}{\langle
  %    1, \pi_{00} \rangle} + C_{00}p_{00}\tbinom{N_{0}}{2} \\ 
    a_n &=  C_{00}p_{00}\tbinom{N_{0}}{2} \\ 
   b_n &= C_{00}p_{00} N_{0} \frac{\sigma_0}{\sqrt{2 \log

@@

%   b_n &= (1 - \tfrac{C_{00}p_{00}}{2} + C_{00}p_{00} N_{0}) \frac{\sigma_0}{\sqrt{2 \log
%     n}}

@@

    a_{n,m} =%  N_{\kappa} \frac{\langle x, \pi_{01} \rangle}{\langle

@@

C_{00} p_{00} \tbinom{N_\kappa}{2} &+ (C_{11}p_{11} - C_{10} p_{10})
\tbinom{\mu_E}{2} \\ &+ (C_{01} p_{01} - C_{00} p_{00}) \mu_E \mu_F 

@@

    b_{n,m} = C_{00} p_{00} N_\kappa \frac{\sigma_{E + F}}{\sqrt{2
        \log{m}}}
    %b_{n,m} = (1 - \tfrac{C_{00} p_{00}}{2} + C_{00} p_{00}
    %N_\kappa)\frac{\sigma_{E + F}}{\sqrt{2 \log{n_1}}}

@@

    \mathbb{P}\Bigl[ \tfrac{X - \mu}{\sigma} \leq z\Bigr]  &= \mathbb{P}[X \leq z

@@

  mean and the sample variance are consistent estimators, the claim
  follows after an application of Slutsky's theorem.

@@

$\phi_\lambda(v)$ for our attributed random graphs model at time $t =
t^{*}$ can be approximated by the locality statistics $Y(v)$ for an
unattributed kidney and egg model. The limiting distribution for the
scan statistics in unattributed kidney-egg graphs had previously been
considered in \cite{rukhin:_limit_distr_graph_scan_statis}. We have
thus provided a sketch of the arguments from
\cite{rukhin:_limit_distr_graph_scan_statis} below, along with some minor
changes to handle the case where the probability of kidney-kidney and
kidney-egg connections are different. \\ \\
Let $G$ be an instance of
$\kappa(n,m,p_{11}, p_{10}, p_{00})$, an unattributed kidney-egg graph
with the probability of egg-egg, egg-kidney, and kidney-kidney
connections being $p_{11}$, $p_{10}$, and $p_{00}$,
respectively. $D(v) = M(v) + W(v)$ is then the degree of $v$ in
$G$. We now show two inequalities relating the tail distribution of

@@

We now consider the term $a_{n,m} - g(v)$. We have

@@

for some $a > 0$. The set $\{v \in [m]\}$ can be partitition into

@@

o(1)$ by using a concentration inequality, e.g., Hoeffding's

@@

    m p_{S_3} \leq m \sum_{\{e,f\} \in S_3} \mathbb{P} \Bigl[Z \leq
